A survey of registration practices among observational researchers using preexisting datasets

### 2023-03-14 manuscript/supplementary_materials.Rmd

# Create histogram of the number of observational studies done
processed %>% 
  # Exclude missing responses
  filter(!is.na(n_studies)) %>% 
  ggplot() +
  aes(x = n_studies) +
  geom_histogram() +
  annotate(geom = "text", x = 200, label = n_studies_missing_text, y = 30) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) +
  labs(
    x = "Number of observational studies done prior using ALSPAC",
    y = "Count"
  ) +
  papaja::theme_apa()
```

>>>>

# Create histogram of the number of observational studies done
processed %>% 
  # Exclude missing responses
  filter(!is.na(n_studies)) %>% 
  ggplot() +
  aes(x = n_studies) +
  geom_histogram(binwidth = 3) +
  # annotate(geom = "text", x = 200, label = n_studies_missing_text, y = 30) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 30)) +
  labs(
    x = "Number of observational studies done prior using ALSPAC",
    y = "Count"
  ) +
  papaja::theme_apa()

valami <- 
  processed %>% 
  # Exclude missing responses
  filter(!is.na(n_studies))

ggplot() +
  geom_histogram(
    data = dplyr::filter(valami, n_studies == 0),
    mapping = aes(x = n_studies), binwidth = 1, color = 'red') +
  geom_histogram(
    data = dplyr::filter(valami, n_studies != 0),
    mapping = aes(x = n_studies), binwidth = 5) +
  # annotate(geom = "text", label = n_studies_missing_text, y = 30) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 40)) +
  labs(
    x = "Number of observational studies done prior using ALSPAC",
    y = "Count"
  ) +
  papaja::theme_apa()
```
